\documentclass[aspectratio=169]{beamer}
\usetheme{Madrid}
\usecolortheme{default}
\usepackage{graphicx}
\usepackage{booktabs}

\title[EcoPulse AI]{EcoPulse AI}
\subtitle{Predictive Intelligence for Renewable Energy Grids}
\author{Team Omnox-Dev}
\date{\today}

\begin{document}

\begin{frame}
    \titlepage
\end{frame}

\begin{frame}{The Problem: Blind Spots in the Grid}
    \begin{itemize}
        \item \textbf{Reactive Culture:} Maintenance occurs \textit{after} catastrophic breakdown (e.g., gearbox shattering).
        \item \textbf{Heavy Losses:} Unexpected downtime in commercial wind turbines costs millions in ungenerated revenue.
        \item \textbf{Invisible Degradation:} Solar panels drop in efficiency continuously due to heat/soiling without clear tracking.
    \end{itemize}
    \vspace{0.5cm}
    \textit{We have thousands of sensors tracking raw data, but we lack the intelligence to predict tomorrow.}
\end{frame}

\begin{frame}{The Solution: EcoPulse AI}
    A real-time Operator Console that ingests live physics telemetry and feeds it directly into proactive Neural Networks.
    \vspace{0.5cm}
    \begin{columns}
        \column{0.5\textwidth}
        \textbf{Features:}
        \begin{itemize}
            \item Real-Time Physics Simulator
            \item Mechanical Failure Predictor (RF)
            \item Trajectory Forecaster (LSTM)
            \item Interactive 3D Spatial Maps
        \end{itemize}
        
        \column{0.5\textwidth}
        \textbf{Value:}
        \begin{itemize}
            \item Orchestrates drone dispatch
            \item Automates Curtailment
            \item Prevents Equipment Fires
        \end{itemize}
    \end{columns}
\end{frame}

\begin{frame}{System Architecture}
    \begin{itemize}
        \item \textbf{Data Pipeline:} Physics models generate synthetic, highly realistic multidimensional datasets every fraction of a second.
        \item \textbf{Machine Learning:} 
        \begin{itemize}
            \item \textbf{Wind:} Decision Tree / Random Forest evaluates non-linear thresholds like \textit{Vibration vs. Rotor Speed}.
            \item \textbf{Solar:} PyTorch LSTM network evaluates historical memory to track \textit{Performance Ratios}.
        \end{itemize}
        \item \textbf{Concurrent Framework:} Atomic OS-level file swaps allow operators to inject "Threats" (Dust Storms, Heatwaves) natively into the UI.
    \end{itemize}
\end{frame}

\begin{frame}{Live Threat Injection Demo}
    \begin{center}
        \Large \textbf{Live Dashboard Transition}
        \vspace{0.5cm} \\
        \normalsize Watch the AI ensemble instantly recognize and flag injected Gearbox Thermal Anomalies in real time.
    \end{center}
\end{frame}

\begin{frame}{Business Impact \& The Future}
    \begin{itemize}
        \item \textbf{Portability:} Can be immediately wrapped around any JSON/CSV outputting standard Industrial SCADA system.
        \item \textbf{Cost Optimization:} Shifting from Reactive to Preventive maintenance saves up to 30\% in gross grid liability costs.
        \item \textbf{Next Steps:} API integration to physical systems (Drone Dispatching, Motorised Tilt Angles).
    \end{itemize}
    \vspace{0.5cm}
    \begin{center}
        \textbf{Thank You.}
    \end{center}
\end{frame}

\end{document}
